Mixture Models for Single Cell Assays

### 2012-02-06 MIMOSA.tex
Added figure for unconstrained model fit to constrained model data

\section*{Results}
\subsection*{Simulations}
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{Figures/simulations} 
   \caption{Performance of the Beta-binomial mixture vs Fisher's exact test in simulated data. Data were simulated from a model with hyper--parameters estimated from day 28, Gag1 stimulated, CD4+, IL2 expressing T--cells in the HVTN054 data set. We simulated 500 observations, with a response rate of 40\%, and increasing numbers of cells, ten times each. The performance, measured by the AUC, of the beta--binomial mixture compared to Fisher's exact test is shown in the first panel, as a function of increasing number of events. The estimated and true prior distributions are shown in the second panel for one simulated data set, with N=150,000 events. The ROC curve for Fisher's exact test and the Beta--binomial model for the same simulated data set are shown in the third panel. The observed vs expected false discovery rate for Fisher's exact test and the Beta--binomial model are shown for the same data set in the fourth panel.}
   \label{fig:simulations}
\end{figure}

>>>>

\section*{Results}
\subsection*{Simulations}
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{Figures/simulations} 
   \caption{Performance of the constrained Beta-binomial mixture vs Fisher's exact test in simulated data from a constrained model. Data were simulated from a constrained model with hyper--parameters estimated from day 28, Gag1 stimulated, CD4+, IL2 expressing T--cells in the HVTN054 data set. We simulated 500 observations, with a response rate of 40\%, and increasing numbers of cells, ten times each. The performance, measured by the AUC, of the constrained beta--binomial mixture compared to Fisher's exact test is shown in the first panel, as a function of increasing number of events. The estimated and true prior distributions are shown in the second panel for one simulated data set, with N=150,000 events. The ROC curve for Fisher's exact test and the constrained Beta--binomial model for the same simulated data set are shown in the third panel. The observed vs expected false discovery rate for Fisher's exact test and the constrained Beta--binomial model are shown for the same data set in the fourth panel.}
   \label{fig:simulations}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{Figures/simulations_negt} 
   \caption{Performance of the unconstrained Beta-binomial mixture (unconstrained model) vs Fisher's exact test in simulated data from a constrained model. Data were simulated from a constrained model with hyper--parameters estimated from day 28, Gag1 stimulated, CD4+, IL2 expressing T--cells in the HVTN054 data set. We simulated 500 observations, with a response rate of 40\%, and increasing numbers of cells, ten times each. The performance, measured by the AUC, of the unconstrained beta--binomial mixture compared to Fisher's exact test is shown in the first panel, as a function of increasing number of events. The estimated and true prior distributions are shown in the second panel for one simulated data set, with N=150,000 events. The ROC curve for Fisher's exact test and the unconstrained Beta--binomial model for the same simulated data set are shown in the third panel. The observed vs expected false discovery rate for Fisher's exact test and the Beta--binomial model are shown for the same data set in the fourth panel.}
   \label{fig:simulations}
\end{figure}
